Just-in-case medications list

### 2024-07-11 just_in_case_bnf_medications.qmd
completed vetting the JIC medications list (v1); need to have it checked by a clinician next (v2)

# Introduction

@@

@@

Note that even exact matches need to be carefully checked as not all formualtions are relevant (specifically combination medicines, for example).

@@

Keep only the analgesics section (0407), not the opioid dependence section (0410).

@@

Query:this occurs in 2 forms, butylbromide (antispasmodic) and hydrobromide (nausea and vertigo) – are both relevant? And in all formualtions (toral, injectable, transdermal patch)

@@

```{r}
# TODO: continue adding these, only the anxiolyitics left!
```

# delete below, scratch area

```{r}

search_bnf(keyword="alfentanil") %>% View()
search_bnf(keyword="meptazinol") %>% View()
search_bnf(keyword="minims atropine sulfate") %>% View()
search_bnf(keyword="minims cyclopentolate hydrochloride") %>% View()
# search_bnf(keyword="glycopyrrolate") %>% View()  # glycopyrronium rather than glycopyrrolate
search_bnf(keyword="glycopyrronium") %>% View()  # lots, uprobably not all relevant
search_bnf(keyword="cyclizine") %>% View()  # nto all relevant
search_bnf(keyword="midazolam") %>% View()  # nto all relevant
search_bnf(keyword="loprazolam") %>% View()  # nto all relevant

## checking the ones that had matches...
search_bnf(keyword="meptazinol") %>% View()  # nto all relevant

search_bnf(keyword="alfentanil") %>% View()

jic_medicines <-
  bind_rows(
    jic_medicines,
    search_bnf(keyword="alfentanil")
  )
```

>>>>

# Introduction {#sec-introduction}

@@

Versions:

- v1 is my first attempt at compiling the codes, without a clinician checking over the codes

@@

Note that even exact matches need to be carefully checked as not all formulations are relevant (specifically combination medicines, for example).

@@

Keep only the analgesics section (0407), not the opioid dependence section (0410) - the latter uses buprenorphine hydrochloride and a buprenorphine hcl/naloxone combination.

@@

Query:this occurs in 2 forms, butylbromide (antispasmodic) and hydrobromide (nausea and vertigo) – are both relevant? And in all formulations (oral, injectable, transdermal patch)

@@

```{r}
# search_bnf(keyword="clobazam") %>% View()

jic_medicines <- add_entries(
  meds = "clobazam", 
  bnf_to_add = search_bnf(keyword="clobazam")
  )
```

### clomethiazole

```{r}
# search_bnf(keyword="clomethiazole") %>% View()

jic_medicines <- add_entries(
  meds = "clomethiazole", 
  bnf_to_add = search_bnf(keyword="clomethiazole")
  )
```

### clonazepam

Keeping only systemic clonazepam (BNF subparagraph “control of epilepsy”) and not parenteral (Clonazepam 1mg/1ml inj ampoules and diluent; subparagraph “drugs used in status epilepticus”)

```{r}
# search_bnf(keyword="clonazepam") %>% View()

jic_medicines <- add_entries(
  meds = "clonazepam", 
  bnf_to_add = search_bnf(keyword="clonazepam") %>%
    filter(bnf_paragraph_code == "040801")
  )
```

### diazepam

Keeping all formulations, oral solution/suspension, rectal solution tube, suppositories, injection ampoules

```{r}
# search_bnf(keyword="diazepam") %>% View()

jic_medicines <- add_entries(
  meds = "diazepam", 
  bnf_to_add = search_bnf(keyword="diazepam")
  )
```

### loprazolam

```{r}
# search_bnf(keyword="loprazolam") %>% View()

jic_medicines <- add_entries(
  meds = "loprazolam", 
  bnf_to_add = search_bnf(keyword="loprazolam")
  )
```

### lorazepam

Keeping all formulations, tablets, oral solution/suspension, injection ampoules

```{r}
# search_bnf(keyword="lorazepam") %>% View()

jic_medicines <- add_entries(
  meds = "lorazepam", 
  bnf_to_add = search_bnf(keyword="lorazepam")
  )
```

### lormetazepam

```{r}
# search_bnf(keyword="lormetazepam") %>% View()

jic_medicines <- add_entries(
  meds = "lormetazepam", 
  bnf_to_add = search_bnf(keyword="lormetazepam")
  )
```

### midazolam

keeping only BNF section 0408 “antiepileptic drugs” and not 1501 ”General anaesthesia”; of 0408, keeping both midazolam maleate (tablets, oral liquid, oral syringe) and midazolam hydrochloride (oral syringe, oral solution); (note: 1501 has injection ampoules and infusion vials, as well as oral solution)

```{r}
# search_bnf(keyword="midazolam") %>% View()

jic_medicines <- add_entries(
  meds = "midazolam", 
  bnf_to_add = search_bnf(keyword="midazolam") %>%
    filter(bnf_section_code == "0408")
  )
```

### nitrazepam

This picks up flunitrazepam (Rohypnol) also, but I didn't include that.

```{r}
# search_bnf(keyword="nitrazepam") %>% View()

jic_medicines <- add_entries(
  meds = "nitrazepam", 
  bnf_to_add = search_bnf(keyword="nitrazepam") %>%
    filter(bnf_chemical_substance_code == "0401010R0")  # keep only nitrazepam, not flunitrazepam
  )
```

### temazepam

```{r}
# search_bnf(keyword="temazepam") %>% View()

jic_medicines <- add_entries(
  meds = "temazepam", 
  bnf_to_add = search_bnf(keyword="temazepam")
  )
```

### trazodone hydrochloride

```{r}
# search_bnf(keyword="trazodone hydrochloride") %>% View()

jic_medicines <- add_entries(
  meds = "trazodone hydrochloride", 
  bnf_to_add = search_bnf(keyword="trazodone hydrochloride")
  )
```

### zopiclone

```{r}
# search_bnf(keyword="zopiclone") %>% View()

jic_medicines <- add_entries(
  meds = "zopiclone", 
  bnf_to_add = search_bnf(keyword="zopiclone")
  )
```

### zolpidem tartrate

```{r}
# search_bnf(keyword="zolpidem tartrate") %>% View()

jic_medicines <- add_entries(
  meds = "zolpidem tartrate", 
  bnf_to_add = search_bnf(keyword="zolpidem tartrate")
  )
```

## Check I've included all of them

```{r}
stopifnot(
  nrow(
    ## this should be an empty table - findings meds that were listed in jic but not in jic_medicines
    jic %>% anti_join(jic_medicines, by = "meds")
  )==0
)
```

# Save resulting file

See @sec-introduction for version listing.

```{r}
write_csv(jic_medicines, file = "./bnf/bnf_codes_just_in_case_v1.csv")  # v1 before SM checked
```
